---
title: "MATH 216 Data Science Final Project (Fall 2016)"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

---
output: 
  html_document: 
    keep_md: yes
---


* Name: Kyra Gray
* Project title: Global Shark Attacks Analysis
* Write-up on [RPubs](http://rpubs.com/kyragray/235161)
* Abstract: 

The analysis conducted in the this project explores data drawm from a global shark attacks database dating back to the 1500s that can be accessed [here](https://www.kaggle.com/teajay/global-shark-attacks) on Kaggle. The data originally comes from the [Global Shark Attack File](http://www.sharkattackfile.net/index.htm) which I have assumed got its data from the [International Shark Attack File](https://www.flmnh.ufl.edu/fish/isaf/home/), due to some specific similarities in the description of the ISAF's database and the data I worked with. The original dataset included 16 original variables and of those 16 the variables that proved most relevant to my anlysis were Year, Type of Attack (provoked vs unprovoked), Country, Area, Location, the Activity was victim was engaging in when the attack occured, Injury, and Fatal (Y/N). 

By creating leaflet plots of the location of each attack, I was able to portray regional trends of where attacks are happening by each variable of interest. Generally, shark attacks occur in the same overall regions across the globe, however there are slight location based trends for attacks that were fatal or occured while the victim was engaging an activity that was Board Involved, Fishing Involved Swimming/Diving. Additionally, the logistic regression model for predicting the fatality of an attack (using Activity, Location, and Type) accurately predicted a fatal attack 70% of the time. 




```{r, echo=FALSE, message=FALSE, warning=FALSE}
#
# Include code for one plot here
#
library(tidyverse)
library(lubridate)
library(Quandl)
library(dplyr)
library(ggplot2)
library(stringr)
library(broom)
library(forcats)
library(ggmap)
library(leaflet)
library(readr)
library(colorspace)

attacks <- read_csv("~/Desktop/Middlebury/Data Science/Final-Project/attacks.csv")
attacks <- attacks %>% 
  tibble::rownames_to_column(var="id_internal")

attacks <- attacks %>%
  ##Renaming Activities 
  mutate(Activity1 = Activity) %>% 
    ##Wading
    mutate(Activity1 = ifelse(grepl("Wading", Activity), "Wading", Activity1)) %>% 
    mutate(Activity1 = ifelse(grepl("wading", Activity), "Wading", Activity1)) %>% 
    ##Standing
    mutate(Activity1 = ifelse(grepl("Standing", Activity), "Standing", Activity1)) %>% 
    mutate(Activity1 = ifelse(grepl("standing", Activity), "Standing", Activity1)) %>% 
    mutate(Activity1 = ifelse(grepl("Stamding", Activity), "Standing", Activity1)) %>% 
    ##Playing
    mutate(Activity1 = ifelse(grepl("Playing", Activity), "Playing", Activity1)) %>% 
    mutate(Activity1 = ifelse(grepl("playing", Activity), "Playing", Activity1)) %>% 
    ##Fell
    mutate(Activity1 = ifelse(grepl("Fell", Activity), "Fell", Activity1)) %>% 
    mutate(Activity1 = ifelse(grepl("fell", Activity), "Fell", Activity1)) %>% 
    mutate(Activity1 = ifelse(grepl("Overboard", Activity), "Fell", Activity1)) %>% 
    mutate(Activity1 = ifelse(grepl("overboard", Activity), "Fell", Activity1)) %>% 
    ##Bathing
    mutate(Activity1 = ifelse(grepl("Bathing", Activity), "Bathing", Activity1)) %>% 
    mutate(Activity1 = ifelse(grepl("bathing", Activity), "Bathing", Activity1)) %>% 
    mutate(Activity1 = ifelse(grepl("Bathe", Activity), "Bathing", Activity1)) %>% 
    mutate(Activity1 = ifelse(grepl("bathe", Activity), "Bathing", Activity1)) %>% 
    mutate(Activity1 = ifelse(grepl("Bath", Activity), "Bathing", Activity1)) %>% 
    mutate(Activity1 = ifelse(grepl("bath", Activity), "Bathing", Activity1)) %>% 
    ##Treading water 
    mutate(Activity1 = ifelse(grepl("Treading water", Activity), "Treading Water", Activity1)) %>% 
    mutate(Activity1 = ifelse(grepl("treading water", Activity), "Treading Water", Activity1)) %>% 
    mutate(Activity1 = ifelse(grepl("Treading", Activity), "Treading Water", Activity1)) %>% 
    mutate(Activity1 = ifelse(grepl("treading", Activity), "Treading Water", Activity1)) %>% 
    ##Washing
    mutate(Activity1 = ifelse(grepl("Washing", Activity), "Washing", Activity1)) %>% 
    mutate(Activity1 = ifelse(grepl("washing", Activity), "Washing", Activity1)) %>% 
    ##Murder
    mutate(Activity1 = ifelse(grepl("Murder", Activity), "Murder", Activity1)) %>% 
    mutate(Activity1 = ifelse(grepl("murder", Activity), "Murder", Activity1)) %>% 
    mutate(Activity1 = ifelse(grepl("Murdered", Activity), "Murder", Activity1)) %>% 
    mutate(Activity1 = ifelse(grepl("murdered", Activity), "Murder", Activity1)) %>% 
    ##Splashing
    mutate(Activity1 = ifelse(grepl("Splashing", Activity), "Splashing", Activity1)) %>% 
    mutate(Activity1 = ifelse(grepl("splashing", Activity), "Splashing", Activity1)) %>% 
    mutate(Activity1 = ifelse(grepl("Splash", Activity), "Splashing", Activity1)) %>% 
    mutate(Activity1 = ifelse(grepl("splash", Activity), "Splashing", Activity1)) %>% 
    ##Walking 
    mutate(Activity1 = ifelse(grepl("Walking", Activity), "Walking", Activity1)) %>% 
    mutate(Activity1 = ifelse(grepl("walking", Activity), "Walking", Activity1)) %>% 
    mutate(Activity1 = ifelse(grepl("Walk", Activity), "Walking", Activity1)) %>% 
    mutate(Activity1 = ifelse(grepl("walk", Activity), "Walking", Activity1)) %>% 
    ##Rowing
    mutate(Activity1 = ifelse(grepl("Rowing", Activity), "Rowing", Activity1)) %>% 
    mutate(Activity1 = ifelse(grepl("rowing", Activity), "Rowing", Activity1)) %>% 
    ##Floating
    mutate(Activity1 = ifelse(grepl("Floating", Activity), "Floating", Activity1)) %>% 
    mutate(Activity1 = ifelse(grepl("floating", Activity), "Floating", Activity1)) %>% 
    ##Paddling
    mutate(Activity1 = ifelse(grepl("Paddling", Activity), "Paddling", Activity1)) %>% 
    mutate(Activity1 = ifelse(grepl("Sculling", Activity), "Paddling", Activity1)) %>% 
    mutate(Activity1 = ifelse(grepl("paddling", Activity), "Paddling", Activity1)) %>% 
    mutate(Activity1 = ifelse(grepl("Paddle", Activity), "Paddling", Activity1)) %>% 
    mutate(Activity1 = ifelse(grepl("paddle", Activity), "Paddling", Activity1)) %>% 
    ##Body Surfing
    mutate(Activity1 = ifelse(grepl("Body Surfing", Activity), "Body Surfing", Activity1)) %>% 
    mutate(Activity1 = ifelse(grepl("Body surfing", Activity), "Body Surfing", Activity1)) %>% 
    #Snorkeling
    mutate(Activity1 = ifelse(grepl("Snorkeling", Activity), "Snorkeling", Activity1)) %>% 
    mutate(Activity1 = ifelse(grepl("snorkeling", Activity), "Snorkeling", Activity1)) %>% 
    ##Kite Boarding
    mutate(Activity1 = ifelse(grepl("Kite Boarding", Activity), "Kite Boarding", Activity1)) %>% 
    mutate(Activity1 = ifelse(grepl("Kite boarding", Activity), "Kite Boarding", Activity1)) %>% 
    mutate(Activity1 = ifelse(grepl("Kite-boarding", Activity), "Kite Boarding", Activity1)) %>% 
    mutate(Activity1 = ifelse(grepl("Kiteboarding", Activity), "Kite Boarding", Activity1)) %>% 
    mutate(Activity1 = ifelse(grepl("Kite-Boarding", Activity), "Kite Boarding", Activity1)) %>%
    ##Canoeing
    mutate(Activity1 = ifelse(grepl("Canoeing", Activity), "Canoeing", Activity1)) %>% 
    mutate(Activity1 = ifelse(grepl("canoeing", Activity), "Canoeing", Activity1)) %>% 
    mutate(Activity1 = ifelse(grepl("canoe", Activity), "Canoeing", Activity1)) %>% 
    mutate(Activity1 = ifelse(grepl("Canoe", Activity), "Canoeing", Activity1)) %>% 
    ##Kayaking
    mutate(Activity1 = ifelse(grepl("Kayaking", Activity), "Kayaking", Activity1)) %>% 
    mutate(Activity1 = ifelse(grepl("kayaking", Activity), "Kayaking", Activity1)) %>% 
    mutate(Activity1 = ifelse(grepl("Kayak", Activity), "Kayaking", Activity1)) %>% 
    mutate(Activity1 = ifelse(grepl("kayak", Activity), "Kayaking", Activity1)) %>% 
    ##Boogie Boarding
    mutate(Activity1 = ifelse(grepl("Boogie Boarding", Activity), "Boogie Boarding", Activity1)) %>% 
    mutate(Activity1 = ifelse(grepl("Boogie boarding", Activity), "Boogie Boarding", Activity1)) %>% 
    mutate(Activity1 = ifelse(grepl("boogie boarding", Activity), "Boogie Boarding", Activity1)) %>% 
    mutate(Activity1 = ifelse(grepl("Body Boarding", Activity), "Boogie Boarding", Activity1)) %>% 
    mutate(Activity1 = ifelse(grepl("Body boarding", Activity), "Boogie Boarding", Activity1)) %>% 
    mutate(Activity1 = ifelse(grepl("Bodyboarding", Activity), "Boogie Boarding", Activity1)) %>% 
    mutate(Activity1 = ifelse(grepl("Body-boarding", Activity), "Boogie Boarding", Activity1)) %>% 
    mutate(Activity1 = ifelse(grepl("body board", Activity), "Boogie Boarding", Activity1)) %>% 
    ##Paddleboarding
    mutate(Activity1 = ifelse(grepl("Paddleboarding", Activity), "Paddleboarding", Activity1)) %>% 
    mutate(Activity1 = ifelse(grepl("Paddle boarding", Activity), "Paddleboarding", Activity1)) %>% 
    mutate(Activity1 = ifelse(grepl("Paddle-boarding", Activity), "Paddleboarding", Activity1)) %>% 
    mutate(Activity1 = ifelse(grepl("Stand-Up Paddleboarding", Activity), "Paddleboarding", Activity1)) %>% 
    mutate(Activity1 = ifelse(grepl("SUP", Activity), "Paddleboarding", Activity1)) %>% 
    mutate(Activity1 = ifelse(grepl("Paddle Boarding", Activity), "Paddleboarding", Activity1)) %>% 
    mutate(Activity1 = ifelse(grepl("Paddleboarding", Activity), "Paddleboarding", Activity1)) %>% 
    ##Jumping
    mutate(Activity1 = ifelse(grepl("Jumping", Activity), "Jumping", Activity1)) %>% 
    mutate(Activity1 = ifelse(grepl("jumping", Activity), "Jumping", Activity1)) %>% 
    mutate(Activity1 = ifelse(grepl("Jumped", Activity), "Jumping", Activity1)) %>% 
    mutate(Activity1 = ifelse(grepl("jumped", Activity), "Jumping", Activity1)) %>% 
    mutate(Activity1 = ifelse(grepl("Jump", Activity), "Jumping", Activity1)) %>% 
    mutate(Activity1 = ifelse(grepl("jump", Activity), "Jumping", Activity1)) %>% 
    ##Sailing
    mutate(Activity1 = ifelse(grepl("Sailing", Activity), "Sailing", Activity1)) %>% 
    mutate(Activity1 = ifelse(grepl("sailing", Activity), "Sailing", Activity1)) %>% 
    mutate(Activity1 = ifelse(grepl("sailboat", Activity), "Sailing", Activity1)) %>% 
    mutate(Activity1 = ifelse(grepl("Sailboat", Activity), "Sailing", Activity1)) %>% 
    ##Raft
    mutate(Activity1 = ifelse(grepl("Raft", Activity), "Raft", Activity1)) %>% 
    mutate(Activity1 = ifelse(grepl("raft", Activity), "Raft", Activity1)) %>% 
    mutate(Activity1 = ifelse(grepl("floatation device", Activity), "Raft", Activity1)) %>% 
    #Boating
    mutate(Activity1 = ifelse(grepl("Boating", Activity), "Boating", Activity1)) %>% 
    mutate(Activity1 = ifelse(grepl("boating", Activity), "Boating", Activity1)) %>% 
    mutate(Activity1 = ifelse(grepl("Boat", Activity), "Boating", Activity1)) %>% 
    mutate(Activity1 = ifelse(grepl("boat", Activity), "Boating", Activity1)) %>% 
    mutate(Activity1 = ifelse(grepl("Yacht", Activity), "Boating", Activity1)) %>% 
    mutate(Activity1 = ifelse(grepl("yachtsman", Activity), "Boating", Activity1)) %>% 
    ##Diving
    mutate(Activity1 = ifelse(grepl("Diving", Activity), "Diving", Activity1)) %>% 
    mutate(Activity1 = ifelse(grepl("diving", Activity), "Diving", Activity1)) %>% 
    mutate(Activity1 = ifelse(grepl("Dived", Activity), "Diving", Activity1)) %>% 
    mutate(Activity1 = ifelse(grepl("dived", Activity), "Diving", Activity1)) %>% 
    mutate(Activity1 = ifelse(grepl("Dive", Activity), "Diving", Activity1)) %>% 
    mutate(Activity1 = ifelse(grepl("dive", Activity), "Diving", Activity1)) %>% 
    ##Swimming
    mutate(Activity1 = ifelse(grepl("Swimming", Activity), "Swimming", Activity1)) %>% 
    mutate(Activity1 = ifelse(grepl("swimming", Activity), "Swimming", Activity1)) %>% 
    mutate(Activity1 = ifelse(grepl("Swim", Activity), "Swimming", Activity1)) %>% 
    mutate(Activity1 = ifelse(grepl("swim", Activity), "Swimming", Activity1)) %>% 
    ##Air or Sea Disaster 
    mutate(Activity1 = ifelse(grepl("Air Disaster", Activity), "Air or Sea Disaster", Activity1)) %>% 
    mutate(Activity1 = ifelse(grepl("Sea Disaster", Activity), "Air or Sea Disaster", Activity1)) %>% 
    mutate(Activity1 = ifelse(grepl("Air disaster", Activity), "Air or Sea Disaster", Activity1)) %>% 
    mutate(Activity1 = ifelse(grepl("Sea disaster", Activity), "Air or Sea Disaster", Activity1)) %>% 
    mutate(Activity1 = ifelse(grepl("air disaster", Activity), "Air or Sea Disaster", Activity1)) %>% 
    mutate(Activity1 = ifelse(grepl("sea disaster", Activity), "Air or Sea Disaster", Activity1)) %>% 
    mutate(Activity1 = ifelse(grepl("Aircraft", Activity), "Air or Sea Disaster", Activity1)) %>% 
    mutate(Activity1 = ifelse(grepl("aircraft", Activity), "Air or Sea Disaster", Activity1)) %>% 
    mutate(Activity1 = ifelse(grepl("Sank", Activity), "Air or Sea Disaster", Activity1)) %>% 
    mutate(Activity1 = ifelse(grepl("sank", Activity), "Air or Sea Disaster", Activity1)) %>% 
    mutate(Activity1 = ifelse(grepl("Explosion", Activity), "Air or Sea Disaster", Activity1)) %>% 
    mutate(Activity1 = ifelse(grepl("explosion", Activity), "Air or Sea Disaster", Activity1)) %>% 
    mutate(Activity1 = ifelse(grepl("burned", Activity), "Air or Sea Disaster", Activity1)) %>% 
    mutate(Activity1 = ifelse(grepl("burning", Activity), "Air or Sea Disaster", Activity1)) %>% 
    mutate(Activity1 = ifelse(grepl("wrecked", Activity), "Air or Sea Disaster", Activity1)) %>% 
    mutate(Activity1 = ifelse(grepl("sinking", Activity), "Air or Sea Disaster", Activity1)) %>% 
    mutate(Activity1 = ifelse(grepl("exploded", Activity), "Air or Sea Disaster", Activity1)) %>% 
    mutate(Activity1 = ifelse(grepl("Adrift", Activity), "Air or Sea Disaster", Activity1)) %>% 
    mutate(Activity1 = ifelse(grepl("crashed", Activity), "Air or Sea Disaster", Activity1)) %>% 
    mutate(Activity1 = ifelse(grepl("plunged", Activity), "Air or Sea Disaster", Activity1)) %>% 
    mutate(Activity1 = ifelse(grepl("sunk", Activity), "Air or Sea Disaster", Activity1)) %>% 
    mutate(Activity1 = ifelse(grepl("torpedoed", Activity), "Air or Sea Disaster", Activity1)) %>% 
    mutate(Activity1 = ifelse(grepl("torpedoes", Activity), "Air or Sea Disaster", Activity1)) %>% 
    mutate(Activity1 = ifelse(grepl("capsized", Activity), "Air or Sea Disaster", Activity1)) %>% 
    mutate(Activity1 = ifelse(grepl("fire", Activity), "Air or Sea Disaster", Activity1)) %>% 
    mutate(Activity1 = ifelse(grepl("Sinking", Activity), "Air or Sea Disaster", Activity1)) %>% 
    mutate(Activity1 = ifelse(grepl("crash", Activity), "Air or Sea Disaster", Activity1)) %>% 
    mutate(Activity1 = ifelse(grepl("seaplane", Activity), "Air or Sea Disaster", Activity1)) %>% 
    mutate(Activity1 = ifelse(grepl("foundered", Activity), "Air or Sea Disaster", Activity1)) %>% 
    mutate(Activity1 = ifelse(grepl("Foundering", Activity), "Air or Sea Disaster", Activity1)) %>% 
    mutate(Activity1 = ifelse(grepl("collided", Activity), "Air or Sea Disaster", Activity1)) %>% 
    mutate(Activity1 = ifelse(grepl("collision", Activity), "Air or Sea Disaster", Activity1)) %>% 
    mutate(Activity1 = ifelse(grepl("Wreck", Activity), "Air or Sea Disaster", Activity1)) %>%
    mutate(Activity1 = ifelse(grepl("wreck", Activity), "Air or Sea Disaster", Activity1)) %>% 
    mutate(Activity1 = ifelse(grepl("accident", Activity), "Air or Sea Disaster", Activity1)) %>% 
    mutate(Activity1 = ifelse(grepl("plane", Activity), "Air or Sea Disaster", Activity1)) %>% 
    ##Surfing
    mutate(Activity1 = ifelse(grepl("Surfing", Activity), "Surfing", Activity1)) %>% 
    mutate(Activity1 = ifelse(grepl("surfing", Activity), "Surfing", Activity1)) %>% 
    mutate(Activity1 = ifelse(grepl("Surf", Activity), "Surfing", Activity1)) %>% 
    mutate(Activity1 = ifelse(grepl("surf", Activity), "Surfing", Activity1)) %>% 
    mutate(Activity1 = ifelse(grepl("surfboard", Activity), "Surfing", Activity1)) %>% 
    mutate(Activity1 = ifelse(grepl("Surfboard", Activity), "Surfing", Activity1)) %>% 
    ##Fishing 
    mutate(Activity1 = ifelse(grepl("Fishing", Activity), "Fishing", Activity1)) %>% 
    mutate(Activity1 = ifelse(grepl("fishing", Activity), "Fishing", Activity1)) %>% 
    mutate(Activity1 = ifelse(grepl("Fisherman", Activity), "Fishing", Activity1)) %>% 
    mutate(Activity1 = ifelse(grepl("Fish", Activity), "Fishing", Activity1)) %>% 
    mutate(Activity1 = ifelse(grepl("fish", Activity), "Fishing", Activity1)) %>% 
    mutate(Activity1 = ifelse(grepl("Spearfishing", Activity), "Fishing", Activity1)) %>% 
    mutate(Activity1 = ifelse(grepl("spearfishing", Activity), "Fishing", Activity1)) %>% 
    mutate(Activity1 = ifelse(grepl("sardines", Activity), "Fishing", Activity1)) %>% 
    mutate(Activity1 = ifelse(grepl("Clamming", Activity), "Fishing", Activity1)) %>% 
    mutate(Activity1 = ifelse(grepl("Crabbing", Activity), "Fishing", Activity1)) %>% 
    mutate(Activity1 = ifelse(grepl("shrimp", Activity), "Fishing", Activity1)) %>% 
    mutate(Activity1 = ifelse(grepl("lobsters", Activity), "Fishing", Activity1)) %>% 
    mutate(Activity1 = ifelse(grepl("whale", Activity), "Fishing", Activity1)) %>% 
    mutate(Activity1 = ifelse(grepl("Hunting", Activity), "Fishing", Activity1)) %>% 
    mutate(Activity1 = ifelse(grepl("hunting", Activity), "Fishing", Activity1)) %>% 
    mutate(Activity1 = ifelse(grepl("Lobstering", Activity), "Fishing", Activity1)) %>% 
    mutate(Activity1 = ifelse(grepl("Netting", Activity), "Fishing", Activity1)) %>% 
    mutate(Activity1 = ifelse(grepl("netting", Activity), "Fishing", Activity1)) %>% 
    mutate(Activity1 = ifelse(grepl("Net", Activity), "Fishing", Activity1)) %>% 
    mutate(Activity1 = ifelse(grepl("net", Activity), "Fishing", Activity1)) %>% 
    mutate(Activity1 = ifelse(grepl("prawns", Activity), "Fishing", Activity1)) %>% 
    mutate(Activity1 = ifelse(grepl("Shrimping", Activity), "Fishing", Activity1)) %>% 
    mutate(Activity1 = ifelse(grepl("dolphins", Activity), "Fishing", Activity1)) %>% 
    mutate(Activity1 = ifelse(grepl("crocodile", Activity), "Fishing", Activity1)) %>% 
    mutate(Activity1 = ifelse(grepl("turtle", Activity), "Fishing", Activity1)) %>% 
    mutate(Activity1 = ifelse(grepl("crabs", Activity), "Fishing", Activity1)) %>% 
    mutate(Activity1 = ifelse(grepl("stingrays?", Activity), "Fishing", Activity1)) %>% 
    mutate(Activity1 = ifelse(grepl("Oystering", Activity), "Fishing", Activity1)) %>% 
    ##Shark
    mutate(Activity1 = ifelse(grepl("Shark", Activity), "Shark", Activity1)) %>% 
    mutate(Activity1 = ifelse(grepl("shark", Activity), "Shark", Activity1)) %>% 
    mutate(Activity1 = ifelse(grepl("Sharks", Activity), "Shark", Activity1)) %>% 
    mutate(Activity1 = ifelse(grepl("sharks", Activity), "Shark", Activity1)) %>% 

  ##Type of attack boating and boat are the same 
  mutate(Type = gsub("Boating", "Boat", Type)) %>% 
  
  ##Renaming injury classification 
  replace_na(list(Injury = "No injury")) %>% 
  mutate(Injury1 = Injury) %>% 
  ##Injury 
  mutate(Injury1 = "Injury") %>% 
  ##No injury
  mutate(Injury1 = ifelse(grepl("No injury", Injury), "No injury", Injury1)) %>% 
  mutate(Injury1 = ifelse(grepl("no injury", Injury), "No injury", Injury1)) %>% 
  ##Fatal
  mutate(Injury1 = ifelse(grepl("FATAL", Injury), "Fatal", Injury1)) %>% 

  ##Cleaning Fatal variable 
  mutate(Fatal= `Fatal (Y/N)`) %>% 
  mutate(Fatal1 = Fatal) %>% 
  mutate(Fatal1= ifelse(grepl("n", Fatal), "N", Fatal1)) %>% 
  mutate(Fatal1= ifelse(grepl("F", Fatal), "Y", Fatal1)) %>% 
  
  ## Making one long location string 
  unite(location_string, Location, Area, Country, sep=" ", remove = FALSE) %>% 
  mutate(new_string = gsub("miles off", "", location_string)) %>% 
  mutate(new_string = gsub("k off", "", new_string)) %>% 
  mutate(new_string = gsub("Off", "", new_string)) %>% 
  mutate(new_string= gsub("[[:digit:]]", "", new_string)) %>% 
  mutate(new_string= gsub("[[:punct:]]", "", new_string))


## making a clean attacks data frame 
attacks_clean <- attacks %>% 
  select(id_internal, 
         Year, 
         Type, 
         Country, 
         Area, 
         Location, 
         location_string,
         new_string, 
         Activity,
         Activity1,
         Sex, 
         Age, 
         Injury,
         Injury1,
         Fatal1, 
         Species)

##Dealing with locations of attacks
attacks_location <- attacks %>% 
  select(Country, Area, Location) %>% 
  unique() %>% 
  na.omit(Country) %>% 
  na.omit(Area) %>% 
  na.omit(Location) %>% 
  unite(location_string, Location, Area, Country, sep=" ", remove = TRUE) 

## getting rid of all the locatiosn with "bad characters 
index_location_good <- Encoding(attacks_location$location_string) == "unknown"
# now we've deleted all rows where the character string was bad
attacks_location <- attacks_location[index_location_good, ]

attacks_location <- attacks_location %>%
  mutate(new_string = gsub("miles off", "", location_string)) %>% 
  mutate(new_string = gsub("k off", "", new_string)) %>% 
  mutate(new_string = gsub("Off", "", new_string)) %>% 
  mutate(new_string= gsub("[[:digit:]]", "", new_string)) %>% 
  mutate(new_string= gsub("[[:punct:]]", "", new_string))

## Geocode Function
## gc <- do.call(rbind, lapply(as.character(attacks_location$location_string), geocode, override_limit = TRUE))
## save(gc, file="location.Rdata")
load("location.Rdata")
attacks_location <- attacks_location %>% mutate(lon=gc$lon, lat=gc$lat)

## Omitting all the locations with no lat or long coords 
attacks_location_na <- attacks_location %>% 
  na.omit(lat)

## Joining so attacks_locations_na will get all the observations 
attacks_location_na <- attacks_location_na %>% 
  left_join(attacks_clean, attacks_location_na, by="new_string")

attacks_location_na <- attacks_location_na %>% 
  select(id_internal,
         Year,
         new_string, 
         lon,
         lat,
         Country,
         Area,
         Location,
         Type,
         Activity1,
         Injury1,
         Fatal1
         ) %>% 

##Renaming/generalizing the categorical buckets for the Activity variable 
  mutate(Activity2 = Activity1) %>% 
##Board Involved 
  ##Body Surfing
  mutate(Activity2 = ifelse(grepl("Body Surfing", Activity1), "Board involved", Activity2)) %>% 
  ##Surfing
  mutate(Activity2 = ifelse(grepl("Surfing", Activity1), "Board involved", Activity2)) %>% 
  ##Boogie Boarding
  mutate(Activity2 = ifelse(grepl("Boogie Boarding", Activity1), "Board involved", Activity2)) %>% 
  ##Kite Boarding
  mutate(Activity2 = ifelse(grepl("Kite Boarding", Activity1), "Board involved", Activity2)) %>% 
  ##Kayaking
  mutate(Activity2 = ifelse(grepl("Kayaking", Activity1), "Board involved", Activity2)) %>% 
  ##Paddleboarding
  mutate(Activity2 = ifelse(grepl("Paddleboarding", Activity1), "Board involved", Activity2)) %>% 
  ##Canoeing
  mutate(Activity2 = ifelse(grepl("Canoeing", Activity1), "Board involved", Activity2)) %>% 
  ###Paddling
  mutate(Activity2 = ifelse(grepl("Paddling", Activity1), "Board involved", Activity2)) %>% 
  
## Fishing Involved 
  mutate(Activity2 = ifelse(grepl("Spearfishing", Activity1), "Fishing involved", Activity2)) %>% 
  mutate(Activity2 = ifelse(grepl("Fishing", Activity1), "Fishing involved", Activity2)) %>% 
  
## Swimming/Diving 
  mutate(Activity2 = ifelse(grepl("Swimming", Activity1), "Swimming/Diving", Activity2)) %>% 
  mutate(Activity2 = ifelse(grepl("Diving", Activity1), "Swimming/Diving", Activity2)) %>% 
  mutate(Activity2 = ifelse(grepl("Snorkeling", Activity1), "Swimming/Diving", Activity2)) %>% 
  mutate(Activity2 = ifelse(grepl("Bathing", Activity1), "Swimming/Diving", Activity2)) %>% 
  mutate(Activity2 = ifelse(grepl("Treading water", Activity1), "Swimming/Diving", Activity2)) %>% 
  mutate(Activity2 = ifelse(grepl("Wading", Activity1), "Swimming/Diving", Activity2)) %>% 
  mutate(Activity2 = ifelse(grepl("Playing", Activity1), "Swimming/Diving", Activity2)) %>% 
  mutate(Activity2 = ifelse(grepl("Splashing", Activity1), "Swimming/Diving", Activity2)) %>% 
  mutate(Activity2 = ifelse(grepl("Fell", Activity1), "Swimming/Diving", Activity2)) %>% 
  mutate(Activity2 = ifelse(grepl("Jumping", Activity1), "Swimming/Diving", Activity2)) %>% 
  mutate(Activity2 = ifelse(grepl("Standing", Activity1), "Swimming/Diving", Activity2)) %>% 
  mutate(Activity2 = ifelse(grepl("Floating", Activity1), "Swimming/Diving", Activity2)) %>% 

## Making an "Other" categorical Activity variable   
  mutate(Activity3 = ifelse(Activity2 == "Board involved", "Board involved", 
                            ifelse(Activity2 == "Fishing involved", "Fishing involved", 
                                   ifelse(Activity2 == "Swimming/Diving", "Swimming/Diving",
                                          ifelse(Activity2 == "Air or Sea Disaster", "Air or Sea Disaster",
                                                 ifelse(Activity2 == "Shark", "Shark", "Other")))))) %>% 
  mutate(Activity3 = ifelse(is.na(Activity3), "Other", Activity3))

pal <- colorFactor(rainbow(6), attacks_location_na$Activity3)

leaflet(attacks_location_na) %>%
  addTiles() %>%
  addCircleMarkers(~lon, ~lat,
                   radius = ~ifelse(Activity3 == "Board involved", 6, 4),
                   color = ~pal(Activity3),
                   stroke = FALSE, fillOpacity = 0.5
  ) %>% 
  addLegend("topleft",
            pal=pal, 
            values = ~Activity3, 
            title = "Activity prior to Attack")

```

